### 2016-03-06 paper/introduction.tex
yasu

\section{Introduction}
Parallel computation has changed the field of Computing.  In the 90s,
most processors had single cores. In 2016, most processors have multiple
cores, often 4 or even 8. Cluster computing further expands the
potential of parallel computation, where one can easily launch a
processing job using hundreds or even thousands of computers in a
cloud. Computer Vision is not an exception in exploiting the powerful
parallel computation.

As image sensor technologies improve, Computer Vision need to deal with
large-scale inference problems more than ever.

>>>>

\section{Introduction}
Parallel computation has changed the field of Computing.  In the 90s,
most processors had single cores. In 2016, most processors have multiple
cores, often 4 or even 8. Cluster computing further expands the
potential of parallel computation, where one can easily launch a
processing job using hundreds or even thousands of computers in a
cloud. Computer Vision is not an exception in exploiting the powerful
parallel computation, where we are in greater demand to solve very large
problems.

parallel computation has been and will be an important

\yasu{mention GPU?}
